Text as Policy: \\ Measuring Policy Similarity through Bill Text Reuse

### 2016-02-14 manuscript/text_reuse.tex
re-arranged sections and added conclusion

\usepackage{graphicx} % to include pictures
\usepackage{subfig} % create subfigures within figures
\usepackage{pdflscape} % e.g. to rotate one page of the document
\usepackage{booktabs} % make better looking tabels with different line types and stuff
\usepackage[left=2.5cm,right=3cm,top=3cm,bottom=2.5cm]{geometry}
\usepackage{fancyhdr} % for pages with custom headers and footers
\usepackage[utf8]{inputenc}
\usepackage{float}
\usepackage{datetime}
\usepackage{natbib}
\usepackage{setspace}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{xr}
\usepackage{subfig}

\setlength{\parindent}{0.0in}
\setlength{\parskip}{2ex plus 0.5ex minus 0.2ex}
\mmddyyyydate
\doublespacing
\externaldocument{tables/ideology_regs.tex}
\externaldocument{tables/ncsl_crosstab.tex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{Considering Policy Similarity}

@@

\section{Data}

We will rely on three main data sources to assess the reliability of text reuse to
identify substantively equivalent bills.

\subsection{Bill text}\\
In order to calculate the alignment scores between bills, we rely on a database collected by Burgess et al. (2015) and the Sunlight foundation. This data base contains approximately 500,000 bills from 2008 to 2015. The available metadata for the bills includes a timestamp for introduction and approval of the bill, the name and party affiliation of the sponsor(s), the state and the bill id.  This collection of bills is based on all bills that are available through the \url{openstates.org} API. Open states is a website maintained by the Sunlight Foundation, in order to increase transparency in state politics. The Sunlight Foundation use web scrapers to access all bills that are available on the websites of legislatures in all US states. This includes enacted legislation as well as bill that is still in the legislative process, or where not enacted. The database contains the bill text as well as additional information on the legislative process for the bill. We have the first and the last version of the bill text, the sponsor of the bill and all legislative action that was taken on the bill.

@@

\subsection{Ideological Scores}\\
For the ideological matching, we rely on latent ideology scores measured by \citep{shor2011}. The data set contains scores for 20738 legislators from 50 state legislatures as well as their party affiliation and their time in office.

\subsection{Ground truth - NCSL Tables}\\

@@

\section{Alignments}

\section{Analysis}

We use three strategies in order to assess the validity of text reuse as a measure of policy equivalence. First, we apply topic models to the sequences that are identified by the SW algorithm as matching sequences. This provides a rough idea of how many of the alignments are substantial and how much procedural language and not substantively significant language gets picked up by the algorithm. Second, we analyze how well the bill similarity aggregated to the state level corresponds with policy diffusion networks identified in previous research \citep{desmarais2015}. And third, we assess the correlation of the distance of the sponsors of a bill dyad and the dyads alignment scores. If substantive policy content, and importantly, the same ideological direction of the provisions is detected by the alignment algorithm, we will expect a high negative correlation between these two measures.
\subsection{NCSL Tables}

@@

@@

@@

\section{Appendix}

>>>>

\usepackage{graphicx} % to include pictures
\usepackage{subfig} % create subfigures within figures
\usepackage{pdflscape} % e.g. to rotate one page of the document
\usepackage{booktabs} % make better looking tabels with different line types and stuff
\usepackage[left=2.5cm,right=3cm,top=3cm,bottom=2.5cm]{geometry}
\usepackage{fancyhdr} % for pages with custom headers and footers
\usepackage[utf8]{inputenc}
\usepackage{float}
\usepackage{datetime}
\usepackage{natbib}
\usepackage{setspace}
\usepackage{booktabs}
\usepackage{color}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{xr}
\usepackage{subfig}

\setlength{\parindent}{0.0in}
\setlength{\parskip}{1.5ex plus 0.5ex minus 0.2ex}
\mmddyyyydate
\doublespacing
\externaldocument{tables/ideology_regs.tex}
\externaldocument{tables/ncsl_crosstab.tex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

\section{Bill Alignments}

In order to calculate the alignment scores between bills, we rely on a database collected by Burgess et al. (2015) and the Sunlight foundation. This data base contains approximately 500,000 bills from 2008 to 2015. The available metadata for the bills includes a timestamp for introduction and approval of the bill, the name and party affiliation of the sponsor(s), the state and the bill id.  This collection of bills is based on all bills that are available through the \url{openstates.org} API. Open states is a website maintained by the Sunlight Foundation, in order to increase transparency in state politics. The Sunlight Foundation use web scrapers to access all bills that are available on the websites of legislatures in all US states. This includes enacted legislation as well as bill that is still in the legislative process, or where not enacted. The database contains the bill text as well as additional information on the legislative process for the bill. We have the first and the last version of the bill text, the sponsor of the bill and all legislative action that was taken on the bill.

@@

{\bf \textcolor{red}{Put in some example allignments}}: Possibly finding a few that appear in bills across several states.

\section{Validation Analysis}

We use three strategies in order to assess the validity of text reuse as a measure of policy equivalence. First, we evaluate whether there is a disproportionately high number of alignments between bills on the same policy area. This is done using the NCSL tables to identify bills on the same policy area.  Second, we analyze how well the bill similarity aggregated to the state level corresponds with policy diffusion networks identified in previous research \citep{desmarais2015}. And third, we assess the correlation of the distance of the sponsors of a bill dyad and the dyads alignment scores. If substantive policy content, and importantly, the same ideological direction of the provisions is detected by the alignment algorithm, we will expect a high negative correlation between these two measures.
\subsection{NCSL Tables}

@@

@@

For the ideological matching, we rely on latent ideology scores measured by \citep{shor2011}. The data set contains scores for 20738 legislators from 50 state legislatures as well as their party affiliation and their time in office.

@@

\section{Applying Bill Similarity: Association with Campaign Contributions}

\section{Conclusion}

Scholarship on public policy and legislative politics relies heavily on measuring the content of legislation, especially with a relative or comparative approach. Manual comparison of bills is prohibitively time consuming when it comes to covering a large proportion of legislation introduced in one or more legislatures. We show that the automated detection of

@@

\section*{Appendix}
